\begin{adjustwidth}{-\extralength}{0cm}
\begin{longtblr}
[
 label={tab:cierre_vacios_implicaciones},
 caption={Analytical closure: recurrent gaps, methodological impact, and operational implications. Own elaboration.}]{
  colspec={X[2.2,l,m] X[0.8,c,m] X[0.8,c,m] X[0.9,c,m] X[2.6,l,m] X[2.8,l,m]},
  width=\fulllength,
  rowhead=1,
  row{1}={font=\bfseries}
}
\toprule
Recurrent gap/limit & k & n & \% & Impact on synthesis & Implication for the proposal \\
\midrule
Unreported data partition \texttt{NR} & 10 & 19 & 52.6 & Introduces uncertainty into performance comparison due to uncontrolled variation in the validation scheme. & Define and justify a fixed evaluation scheme (\texttt{train/val/test} or cross-validation), with full traceability of its application. \\
Unreported defuzzification & 8 & 19 & 42.1 & Hinders reproducibility of the inferential core and technical attribution of performance to fuzzy design. & Specify the defuzzification method and associated parameterization as a required pipeline component. \\
Missing comparator \texttt{NR} & 4 & 19 & 21.1 & Reduces the comparative validity of improvement claims against alternative approaches. & Include a minimum benchmark and a homogeneous criterion for quantitative comparison in experimentation. \\
Unreported improvement \texttt{NR} & 4 & 19 & 21.1 & Limits interpretation of incremental contribution by not making the magnitude of gain explicit. & Report absolute and relative improvement over the baseline under equivalent metrics and conditions. \\
Metric heterogeneity (without a single core) & 11 & 19 & 57.9 & Fragments cross-study reading and increases reporting heterogeneity across studies. & Establish a base metric set (\texttt{MSE/RMSE/MAE} and, when applicable, \texttt{Accuracy}) for mandatory reporting. \\
\bottomrule
\end{longtblr}
\end{adjustwidth}