\section{Introduction}

Air pollution is recognized as a major public health problem and, in urban contexts, a very large share of the population remains exposed to concentrations that do not comply with health-protective standards \cite{PROB01}. In this scenario, risk communication cannot rely only on pollutant concentration series, because the direct reading of such data is not easily accessible to the general population and complicates its use by public authorities and technical operators; for this reason, air quality index systems have become mechanisms for translating atmospheric conditions into understandable messages about risk and health protection \cite{PROB02,PROB03}. However, this interpretive layer is still far from uniform: early reviews of pollution indices already documented considerable structural diversity among calculation systems and reported categories \cite{PROB02}, and later studies showed that approaches based on a single dominant pollutant may underestimate risk severity when several pollutants coexist at dangerous levels or when the focus shifts toward aggregated health effects \cite{PROB04,PROB05}. This limitation becomes more relevant when air-quality assessment is expected to support real-time or near-real-time monitoring over broader urban areas. In that setting, the literature already points to the growing use of sensor-based and wireless monitoring systems, but also to persistent challenges related to deployment conditions, calibration, and measurement reliability \cite{PROB06,PROB07}.

Within this context, fuzzy logic is an alternative when the phenomenon to be modeled does not lend itself easily to deterministic descriptions, since its formulation relies on linguistic variables, fuzzy conditional rules, and approximate inference mechanisms specifically oriented to the treatment of complex or ill-defined systems \cite{ART03}. Recent studies have already brought this conceptual basis into the air-quality domain, although with different purposes and scopes: it has been applied to fuzzy indoor air-quality classification \cite{ART04}, to environmental control and ventilation automation in enclosed spaces \cite{ART05}, to IoT monitoring with classification into ISPU/AQI categories \cite{ART06}, in real-time evaluation of multiple pollutants in smart-city environments \cite{ART07}, and to route optimization and efficient operation of WSN architectures for urban air monitoring \cite{ART08}. This breadth of applications shows that the use of fuzzy inference in air-quality monitoring is no longer marginal. It also indicates that the field has evolved through heterogeneous decisions regarding input variables, fuzzy-system type, deployment scale, technological architecture, and validation approach \cite{ART04,ART05,ART06,ART07,ART08}. From a synthesis perspective, this dispersion makes it difficult to identify which configurations recur, which design decisions are comparable, and how transferable the reported results are across implementation contexts \cite{ART04,ART05,ART06,ART07,ART08}.

This heterogeneity justifies a dedicated systematic review. AQI-oriented studies have shown that air-quality interpretation remains affected by comparability problems across indices, pollutants, aggregation rules, and risk categories \cite{ART01,ART02}. At the same time, recent monitoring studies show the expansion of sensor-based, IoT, and WSN-based implementations intended to support real-time or near-real-time observation under concrete deployment conditions \cite{PROB06,ART07,ART08}. Within that broader landscape, the studies that incorporate fuzzy logic already show a technically diverse field, but one that is still reported through uneven combinations of variables, fuzzy-system configurations, architectures, and performance criteria \cite{ART04,ART05,ART06,ART07,ART08}. Under these conditions, a structured review is methodologically appropriate and feasible, since the domain offers a recent and identifiable body of primary studies that can be examined using Kitchenham's review procedure \cite{kitchenham2007}.

The closest antecedents already make it possible to position this review more precisely. On the AQI side, Priti and Kumar \cite{ART01} review index models developed between 1960 and 2021 and compare them through pollutants considered, averaging times, calculation methods, aggregation modes, scales, and categories. Suman \cite{ART02} likewise emphasizes that large monitoring datasets do not easily communicate air-quality status on their own and discusses AQI as a mechanism for translating pollutant concentrations into interpretable information about exposure and health risk. Murena \cite{PROB08} brings that discussion closer to an applied urban setting by developing an index for a large metropolitan area, showing how air-quality representation depends on the way pollutants are combined and interpreted in practice. These studies establish a clear antecedent for the problem of comparability and interpretation, but they do not focus on fuzzy inference or on the operational structure of real-time monitoring platforms.

The applied antecedents are closer to the technical core of this review, but they do so from specific entry points. Seibert et al. \cite{ART04} compare five fuzzy classifiers for indoor air-quality classification using an open dataset, with emphasis on uncertainty handling and classification performance. Bushnag \cite{ART05} integrates fuzzy logic into an Arduino-based system for monitoring and controlling indoor air quality, temperature, and humidity through ventilation adjustment. Andrianto et al. \cite{ART06} propose an IoT system with Mamdani fuzzy logic that combines PM$_{2.5}$, PM$_{10}$, and CO measurements to generate ISPU/AQI categories in real time. Saleem et al. \cite{ART07} extend the scope to a smart-city monitoring model based on SO$_2$, NO$_2$, CO, O$_3$, and PM$_{10}$, explicitly framing fuzzy inference as part of a real-time urban monitoring setting. Lingaraj et al. \cite{ART08}, in turn, address WSN-based air pollution monitoring from the perspective of routing efficiency, energy consumption, delay, and packet loss in smart-city deployments. These studies confirm that fuzzy logic is already being used in air-quality monitoring, but they do so through bounded objectives and heterogeneous configurations, leaving open a cross-study synthesis of input variables, fuzzy-system design decisions, platform implementation, and evaluation practices. Table~\ref{tab:antecedentes_intro} summarizes these antecedents according to their main contribution, their proximity to the problem studied, and the aspect they still leave open in relation to the present review.

\begin{adjustwidth}{-\extralength}{0cm}
\input{assets/tablas/introduction/antecedentes_intro.tex}
\end{adjustwidth}
The comparison summarized in Table~\ref{tab:antecedentes_intro} shows that the current difficulty arises from the fragmented way in which evidence has been reported across AQI reviews and applied fuzzy-monitoring developments. In the antecedents reviewed, decisions about input variables, fuzzy-system design, real-time monitoring architecture, and performance evaluation are distributed across studies with different scopes and limited possibility for cross-reading \cite{ART01,ART02,PROB08,ART04,ART05,ART06,ART07,ART08}. This dispersion makes it difficult to establish which configurations recur, which methodological decisions are comparable, and which criteria could support a more consistent interpretation of the available evidence \cite{ART01,ART02,ART04,ART05,ART06,ART07,ART08}.

In response to this need, this study aims to analyze systematically how fuzzy-logic-based inference systems are used in real-time monitoring platforms to evaluate urban air quality. The research question guiding the review is the following: \textbf{How are fuzzy-logic-based inference systems used in real-time monitoring platforms to evaluate urban air quality and the associated risks?}

Based on this question, the remainder of the article is organized as follows. Section 2 describes the systematic review methodology, including the PICo framework, search strategy, study-selection process, quality assessment procedure, and data extraction and synthesis design. Section 3 presents the results of the review, organized according to the analytical directives that examine input variables and pollutants, fuzzy-system design decisions, platform implementation in real-time monitoring, and evaluation practices. Section 4 interprets these findings in relation to the antecedents and discusses their methodological and operational implications. Finally, Section 5 presents the conclusions and future research directions.
